Mental Health of U.S. Citizens During the COVID-19 Pandemic

### 2022-03-21 outputs/paper/paper.Rmd
graph size

```{r fig1, warning=FALSE, fig.cap="Mental Health - Male Vs Female", message = FALSE, echo=FALSE, fig.width=5, fig.height=5}
# Percent Graph - Mental health - Male Vs Female
gss2021 %>% filter(!is.na(`Mental Health`), !is.na(sex_group)) %>% ggplot(aes(x= `Mental Health`,  group=sex_group)) +
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
  geom_text(aes( label = scales::percent(..prop..),
                 y= ..prop.. ), stat= "count", vjust = -.5) +
  labs(y = "Percent", x = 'Mental Health', title = 'Mental Health: Male vs. Female') +
  facet_grid(~sex_group) +
  scale_y_continuous(labels = scales::percent) + theme(legend.position="none") + scale_fill_brewer(palette = "Spectral")
```

@@

```{r fig2, warning=FALSE, fig.cap="Mental Health – Physical Health", message = FALSE, echo=FALSE, fig.width=5, fig.height=5}
# Percent Graph Physical health - Good Mental health vs Bad Mental Health
gss2021 %>% filter(!is.na(`Mental Health`), !is.na(sex_group), !is.na(`Physical Health`)) %>%
  ggplot(aes(x= `Physical Health`,  group= `Mental Health`)) +
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
  geom_text(aes( label = scales::percent(..prop..),
                 y= ..prop.. ), stat= "count", vjust = -.5) +
  labs(y = "Percent", fill="Physical Health", x = 'Physical Health', title = "Mental Health vs. Physical Health" ) +
  facet_grid(~`Mental Health` , labeller = label_both) +
  scale_y_continuous(labels = scales::percent) + theme(legend.position="none") + scale_fill_brewer(palette = "Spectral")
```

@@

```{r fig3, warning=FALSE, fig.cap="Physical Health Comparison of Male Vs. Female with Poor Mental Health", message = FALSE, echo=FALSE, fig.width=7, fig.height=6}
# Percent Graph - Poor Mental health = Physical health within Sex_Group comparison
gss2021 %>% filter(!is.na(`Mental Health`), !is.na(sex_group), !is.na(`Physical Health`), `Mental Health` =='Not Good') %>%
  ggplot(aes(x= `Physical Health`,  group=sex_group)) +
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
  geom_text(aes( label = scales::percent(..prop..),
                 y= ..prop.. ), stat= "count", vjust = -.5) +
  labs(y = "Percent", x="Physical Health", title = "Physical Health Comparison of Male Vs. Female with Poor Mental Health") +
  facet_grid(~sex_group) +
  scale_y_continuous(labels = scales::percent) + theme(legend.position="none") + scale_fill_brewer(palette = "Spectral")
```

@@

```{r fig4, warning=FALSE, fig.cap="Mental Health – Age Groups", message = FALSE, echo=FALSE, fig.width=7, fig.height=5}
# Percent Graph - Mental health (Age Group Analysis)
gss2021 %>% filter(!is.na(`Mental Health`),!is.na(`Age Group`)) %>%
  ggplot(aes(x= `Mental Health`,  group=`Age Group`)) +
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
  geom_text(aes( label = scales::percent(..prop..),
                 y= ..prop.. ), stat= "count", vjust = -.5) +
  labs(y = "Percent", x="Mental Health", title = "Mental Health: Comparison of Different Age Groups") +
  facet_grid(~`Age Group`, labeller = label_both) +
  scale_y_continuous(labels = scales::percent) + theme(legend.position="none") + scale_fill_brewer(palette = "Spectral")
```

@@

```{r fig5, warning=FALSE, fig.cap="Mental Health – Sexual Orientation", message = FALSE, echo=FALSE, fig.width=5, fig.height=5}
# Percent Graph - Mental health (Sexual Orientation Analysis)
gss2021 %>% filter(!is.na(`Mental Health`), !is.na(sexual_orientation)) %>%
  ggplot(aes(x= `Mental Health`,  group=sexual_orientation)) +
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
  geom_text(aes( label = scales::percent(..prop..),
                 y= ..prop.. ), stat= "count", vjust = -.5) +
  labs(y = "Percent", x="Mental Health", title = "Mental Health: Heterosexual vs. LGBTQ+") +
  facet_grid(~sexual_orientation) +
  scale_y_continuous(labels = scales::percent) + theme(legend.position="none") + scale_fill_brewer(palette = "Spectral")
```

@@

```{r fig6, warning=FALSE, fig.cap="Mental Health – Social Class", message = FALSE, echo=FALSE, fig.width=9, fig.height=5}
# 'Mental Health: Comparison of Different Social Classes'
gss2021 %>% filter(!is.na(`Mental Health`), !is.na(`Social Class`)) %>% ggplot(aes(x= `Mental Health`,  group= `Social Class`))+
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
  geom_text(aes( label = scales::percent(..prop..),
                 y= ..prop.. ), stat= "count", vjust = -.5) +
  labs(y = "Percent", fill="mntl_poor", title = 'Mental Health: Comparison of Different Social Classes') +
  facet_grid(~factor(`Social Class`, levels = c('lower', 'working','lower middle', 'middle', 'upper middle', 'upper'))) +
  scale_y_continuous(labels = scales::percent) + theme(legend.position="none") + scale_fill_brewer(palette = "Spectral")
```

@@

```{r fig7, warning=FALSE, fig.cap="Mental Health – Total Family Income", message = FALSE, echo=FALSE, fig.width=8, fig.height=5}
# 'Mental Health: Comparison by Total Family Income'
gss2021 %>% filter(!is.na(`Mental Health`), !is.na(Income)) %>%  ggplot(aes(x= `Mental Health`,  group=Income))+
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
  geom_text(aes( label = scales::percent(..prop..),
                 y= ..prop.. ), stat= "count", vjust = -.5) +
  labs(y = "Percent" , title = 'Mental Health: Comparison by Total Family Income') +
  facet_grid(~factor(Income, levels = c('< $10,000', "$10,000 - $20,000", "$20,000 - $40,000", "$40,000 - $60,000", "$60,000 - $90,000", "> $90,000"))) +
  scale_y_continuous(labels = scales::percent) + theme(legend.position="none") + scale_fill_brewer(palette = "Spectral")
```

@@

```{r fig8, warning=FALSE, fig.cap="Mental Health – Age When First Child was Born", message = FALSE, echo=FALSE, fig.width=8, fig.height=5}
#  "Mental Health: Comparison by age when first child was born"
gss2021 %>% filter(!is.na(`Mental Health`), !is.na(`Kid Born`))  %>% ggplot(aes(x= `Mental Health`,  group=`Kid Born`))+
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
  geom_text(aes( label = scales::percent(..prop..),
                 y= ..prop.. ), stat= "count", vjust = -.5) +
  labs(y = "Percent", title = "Mental Health: Comparison by Age When First Child was Born") +
  facet_grid(~`Kid Born`) +
  scale_y_continuous(labels = scales::percent) + theme(legend.position="none") + scale_fill_brewer(palette = "Spectral")
```

>>>>

```{r fig1, warning=FALSE, fig.cap="Mental Health - Male Vs Female", message = FALSE, echo=FALSE, fig.width=5, fig.height=5, out.width='50%', fig.align="center"}
# Percent Graph - Mental health - Male Vs Female
gss2021 %>% filter(!is.na(`Mental Health`), !is.na(sex_group)) %>% ggplot(aes(x= `Mental Health`,  group=sex_group)) +
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
  geom_text(aes( label = scales::percent(..prop..),
                 y= ..prop.. ), stat= "count", vjust = -.5) +
  labs(y = "Percent", x = 'Mental Health', title = 'Mental Health: Male vs. Female') +
  facet_grid(~sex_group) +
  scale_y_continuous(labels = scales::percent) + theme(legend.position="none") + scale_fill_brewer(palette = "Spectral")
```

@@

```{r fig2, warning=FALSE, fig.cap="Mental Health – Physical Health", message = FALSE, echo=FALSE, fig.width=5, fig.height=5, out.width='50%', fig.align="center"}
# Percent Graph Physical health - Good Mental health vs Bad Mental Health
gss2021 %>% filter(!is.na(`Mental Health`), !is.na(sex_group), !is.na(`Physical Health`)) %>%
  ggplot(aes(x= `Physical Health`,  group= `Mental Health`)) +
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
  geom_text(aes( label = scales::percent(..prop..),
                 y= ..prop.. ), stat= "count", vjust = -.5) +
  labs(y = "Percent", fill="Physical Health", x = 'Physical Health', title = "Mental Health vs. Physical Health" ) +
  facet_grid(~`Mental Health` , labeller = label_both) +
  scale_y_continuous(labels = scales::percent) + theme(legend.position="none") + scale_fill_brewer(palette = "Spectral")
```

@@

```{r fig3, warning=FALSE, fig.cap="Physical Health Comparison of Male Vs. Female with Poor Mental Health", message = FALSE, echo=FALSE, fig.width=7, fig.height=6, out.width='50%', fig.align="center"}
# Percent Graph - Poor Mental health = Physical health within Sex_Group comparison
gss2021 %>% filter(!is.na(`Mental Health`), !is.na(sex_group), !is.na(`Physical Health`), `Mental Health` =='Not Good') %>%
  ggplot(aes(x= `Physical Health`,  group=sex_group)) +
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
  geom_text(aes( label = scales::percent(..prop..),
                 y= ..prop.. ), stat= "count", vjust = -.5) +
  labs(y = "Percent", x="Physical Health", title = "Physical Health Comparison of Male Vs. Female with Poor Mental Health") +
  facet_grid(~sex_group) +
  scale_y_continuous(labels = scales::percent) + theme(legend.position="none") + scale_fill_brewer(palette = "Spectral")
```

@@

```{r fig4, warning=FALSE, fig.cap="Mental Health – Age Groups", message = FALSE, echo=FALSE, fig.width=7, fig.height=5, out.width='80%', fig.align="center"}
# Percent Graph - Mental health (Age Group Analysis)
gss2021 %>% filter(!is.na(`Mental Health`),!is.na(`Age Group`)) %>%
  ggplot(aes(x= `Mental Health`,  group=`Age Group`)) +
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
  geom_text(aes( label = scales::percent(..prop..),
                 y= ..prop.. ), stat= "count", vjust = -.5) +
  labs(y = "Percent", x="Mental Health", title = "Mental Health: Comparison of Different Age Groups") +
  facet_grid(~`Age Group`, labeller = label_both) +
  scale_y_continuous(labels = scales::percent) + theme(legend.position="none") + scale_fill_brewer(palette = "Spectral")
```

@@

```{r fig5, warning=FALSE, fig.cap="Mental Health – Sexual Orientation", message = FALSE, echo=FALSE, fig.width=5, fig.height=5, out.width='45%', fig.align="center"}
# Percent Graph - Mental health (Sexual Orientation Analysis)
gss2021 %>% filter(!is.na(`Mental Health`), !is.na(sexual_orientation)) %>%
  ggplot(aes(x= `Mental Health`,  group=sexual_orientation)) +
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
  geom_text(aes( label = scales::percent(..prop..),
                 y= ..prop.. ), stat= "count", vjust = -.5) +
  labs(y = "Percent", x="Mental Health", title = "Mental Health: Heterosexual vs. LGBTQ+") +
  facet_grid(~sexual_orientation) +
  scale_y_continuous(labels = scales::percent) + theme(legend.position="none") + scale_fill_brewer(palette = "Spectral")
```

@@

```{r fig6, warning=FALSE, fig.cap="Mental Health – Social Class", message = FALSE, echo=FALSE, fig.width=9, fig.height=5, out.width='80%', fig.align="center"}
# 'Mental Health: Comparison of Different Social Classes'
gss2021 %>% filter(!is.na(`Mental Health`), !is.na(`Social Class`)) %>% ggplot(aes(x= `Mental Health`,  group= `Social Class`))+
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
  geom_text(aes( label = scales::percent(..prop..),
                 y= ..prop.. ), stat= "count", vjust = -.5) +
  labs(y = "Percent", fill="mntl_poor", title = 'Mental Health: Comparison of Different Social Classes') +
  facet_grid(~factor(`Social Class`, levels = c('lower', 'working','lower middle', 'middle', 'upper middle', 'upper'))) +
  scale_y_continuous(labels = scales::percent) + theme(legend.position="none") + scale_fill_brewer(palette = "Spectral")
```

@@

```{r fig7, warning=FALSE, fig.cap="Mental Health – Total Family Income", message = FALSE, echo=FALSE, fig.width=8, fig.height=5, out.width='80%', fig.align="center"}
# 'Mental Health: Comparison by Total Family Income'
gss2021 %>% filter(!is.na(`Mental Health`), !is.na(Income)) %>%  ggplot(aes(x= `Mental Health`,  group=Income))+
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
  geom_text(aes( label = scales::percent(..prop..),
                 y= ..prop.. ), stat= "count", vjust = -.5) +
  labs(y = "Percent" , title = 'Mental Health: Comparison by Total Family Income') +
  facet_grid(~factor(Income, levels = c('< $10,000', "$10,000 - $20,000", "$20,000 - $40,000", "$40,000 - $60,000", "$60,000 - $90,000", "> $90,000"))) +
  scale_y_continuous(labels = scales::percent) + theme(legend.position="none") + scale_fill_brewer(palette = "Spectral")
```

@@

```{r fig8, warning=FALSE, fig.cap="Mental Health – Age When First Child was Born", message = FALSE, echo=FALSE, fig.width=8, fig.height=5, out.width='80%', fig.align="center"}
#  "Mental Health: Comparison by age when first child was born"
gss2021 %>% filter(!is.na(`Mental Health`), !is.na(`Kid Born`))  %>% ggplot(aes(x= `Mental Health`,  group=`Kid Born`))+
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
  geom_text(aes( label = scales::percent(..prop..),
                 y= ..prop.. ), stat= "count", vjust = -.5) +
  labs(y = "Percent", title = "Mental Health: Comparison by Age When First Child was Born") +
  facet_grid(~`Kid Born`) +
  scale_y_continuous(labels = scales::percent) + theme(legend.position="none") + scale_fill_brewer(palette = "Spectral")
```
